%-------------------------
% Resume in Latex
% Author : Sai Anand K
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Sai Anand K} \\ \vspace{1pt}
    \small 7034758905 $|$ \href{mailto:saianandk2003@gmail.com}{{saianandk2003@gmail.com}} $|$ 
    \href{https://linkedin.com/in/saianandk}{{linkedin.com/in/saianandk}} $|$
    \href{https://github.com/SAI4587}{{github.com/SAI4587}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {School of Engineering, CUSAT}{Kochi, Kerala}
      {Bachelor of Computer Science}{Nov. 2021 -- Present}
    \resumeSubheading
      {Rahmania HSS For Handicapped}{Kozhikode, Kerala}
      {Higher Secondary}{June. 2019 -- March 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI/ML Engineer Intern}{June 2024 -- Present}
      {Dataequinox Technology and Research Private Limited}{Koratty, Kerala}
      \resumeItemListStart
        \resumeItem{Chatbot Development for E-Commerce: Designed and implemented scalable chatbots, overseeing the entire process from front-end user interface to back-end logic.}
        \resumeItem{Model Training and Optimization: Conducted extensive model training and fine-tuning, achieving significant improvements in AI-driven application performance.}
        \resumeItem{Applied Prompt Engineering Techniques: Applied advanced prompt engineering with Gen AI , Cohere AI and LLama to enhance the accuracy of product recommendation systems and feedback for customer care chatbot.}
        \resumeItem{Developed and Fine-Tuned Advanced Language Models: Worked with cutting-edge models like Google Gen AI, Llama 3, and Mistral to build and fine-tune machine learning models for various applications, including product recommendation systems and multilabel classification.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{PDF Chatbot Application} $|$ \emph{Python, Streamlit, Llama API, Google Gemini, PyPDF2}}{}
          \resumeItemListStart
            \resumeItem{Developed a PDF chatbot application using Streamlit, integrating Llama API and Google’s Gemini models to generate accurate, context-aware responses from PDF content.}
            \resumeItem{Implemented efficient text extraction using PyPDF2, optimized to handle PDF files of up to 200 MB, with a high accuracy rate of 95\% in answering document-related questions.}
            \resumeItem{Deployed the application on a streamlit platform, allowing real-time interaction and demonstrating scalability with concurrent user handling capabilities.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{AI Pac-Man Agent} $|$ \emph{PyTorch, Deep Q-Networks, Convolutional Neural Networks, Gymnasium}}{}
    \resumeItemListStart
        \resumeItem{Developed a deep Q-network (DQN) agent using convolutional neural networks to play Ms. Pac-Man, achieving a high average score.}
        \resumeItem{Implemented a four-layer CNN architecture in PyTorch to process game frames and predict optimal actions.}
        \resumeItem{Trained the model using Gymnasium's environment, with adaptive epsilon-greedy policy for action selection.}
        \resumeItem{Visualized model performance by generating gameplay videos with the trained agent.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Care Connect} $|$ \emph{Flutter, Firebase, Dart, Kotlin}}{}
          \resumeItemListStart
            \resumeItem{Built an app to monitor phone inactivity of people under isolation, old people, etc.}
            \resumeItem{Implemented scream and fall detection along with pill reminders.}
            \resumeItem{Stored data and implemented login using firebase.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeItemListStart
      \resumeItem{Artificial Intelligence A-Z 2024 Build 7 AI LLM ChatGPT (Issued May 2024)}
      \resumeItem{C++ Programming - Intermediate - G-Tec Computer Education (Issued May 2019)}
      \resumeItem{Computer Hardware - G-Tec Computer Education (Issued May 2018)}
      \resumeItem{Computer Operation - G-Tec Computer Education (Issued May 2013)}
    \resumeItemListEnd
  \resumeSubHeadingListEnd







%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++} \\
     \textbf{Frameworks}{: TensorFlow, PyTorch, Scikit-Learn, Streamlit} \\
     \textbf{Developer Tools}{: Git, VS Code, PyCharm, Google Gen AI, Cohere AI, Mistral AI, GPT-4, Colab Notebook} \\
     \textbf{Libraries}{: DistilBERT, pandas, NumPy, Matplotlib, Keras, Spacy, Hugging Face, transformers, KeyBERT}
    }}
 \end{itemize}

 %-------------------------------------------
\end{document}


